Are iPhone users more secure when using mobile enterprise systems?

### 2021-04-15 outputs/paper/paper.Rmd
update

---
title: "Are iPhone users more secure when using mobile enterprise systems?"
subtitle: "The difference of the perceived security of Enterprise Systems between IOS and Android users"
author: "Yang Wu"
header-includes:
 - \usepackage{float}
 - \floatplacement{figure}{H}
 - \floatplacement{table}{H}
thanks: "Code and data are available at: https://github.com/yangg1224/Security-of-Enterprise-System.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Organizations are adopting mobile technologies for various business applications including Enterprise system (ES) to increase the flexibility and to gain sustainable competitive advantage. At the same time, end-users are exposed to security issues when using mobile technologies. Users’ usage habits and users’ attitudes towards those potential security issues would have a significant impact to the perceived security of ES. Here comes the question: will iPhone users have higher perceived security than Android users? Through the propensity score matching and regression model, we have the answer. "
output:
  bookdown::pdf_document2:
toc: TRUE
bibliography: references.bib
---

@@

# Data
## Data collection

# Model
## T-test
## correlation model
## propensity score matching
## regression model

>>>>

---
title: "Are iPhone users more secure when using mobile enterprise systems?"
subtitle: "The difference of the perceived security of Enterprise Systems between IOS and Android users"
author: "Yang Wu"
header-includes:
 - \usepackage{float}
 - \floatplacement{figure}{H}
 - \floatplacement{table}{H}
thanks: "Code and data are available at: https://github.com/yangg1224/Security-of-Enterprise-System.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Organizations are adopting mobile technologies for various business applications including Enterprise system (ES) to increase the flexibility and to gain sustainable competitive advantage. At the same time, end-users are exposed to security issues when using mobile technologies. Users’ usage habits and users’ attitudes towards those potential security issues would have a significant impact to the perceived security of ES. Here comes the question: will iPhone users have higher perceived security than Android users? Through the propensity score matching and regression model, we have the answer. \\par \\textbf{Keywords:} Security Issues; Perceived security measurement; iPhone & Android; Matching "

output:
  bookdown::pdf_document2:
toc: TRUE
bibliography: references.bib
---

@@

# Data

## Intervention

To accomplish the research objectives, the author did a literature review on perceived security of mobile Enterprise System (ES). Based on the current research findings, the author concludes that there are five main categories of security issues when using mobile ES, which are mobile device issues, wireless network issues, cloud computing issues, application-level issues, and data access level issues. Different mobile phone users would have different attitudes and usage habits towards those five areas security issues, which greatly affect the perceived security of the ES. In order to test how different those impact on the iPhone and Android users, the author plan to divide people into two groups. The intervention of this research is using iPhone as mobile device. The treated group will be people who use iPhone (IOS) to operate the ES, and people in the control group will be those who use Android (Huawei, Samsung, Mi, and so on).

## Data collection

An online questionnaire survey is the chosen method for collecting data from Mobile ES users. Compared with other methods, the major advantages of the online questionnaire are saving time, money, and manpower. Considering this research need to do a large quantity of data collection, the questionnaire is the only suitable method. The author conducted the online questionnaire survey one year ago under the guidance of the research method class.

Through the agency of Chinese online questionnaire platform ‘Wenjuan Xing’ and the researcher’s personal relationship with certain companies, the author sends out around 800 online questionnaires randomly and 240 personal administered questionnaires. The personally administered survey is useful to increase the response rate and to enhance the data quality. The email reminders were sent for every ten days to encourage the potential participants to fill in their responses.

The respondents were asked to do a demographics survey which includes age, gender, occupation, years of experience, name of the ES systems used, functions or modules of Mobile ES, Brand of the mobile devices used to access the ES, and ownership of the device. The questionnaire also has items for measuring users’ attitudes and usage habits on various security issues and perceived security of ES mobility. The data was collected by using an interval scale (0-strongly disagree to 10-strongly agree). The collected data was used for calculating the measures of central tendency (e.g. arithmetic mean), validating the hypotheses by using correlation, propensity score matching, multiple regression and other statistical analysis.

By the end of the survey period, data had been collected from 344 participants. As a result, the overall response rate is 33%. Among 344 responses, 13 responses were rejected on account of too much missing data. Therefore, 331 useable online questionnaire data were obtained and used for data analysis.

# Model

```{r echo=FALSE}
####read the clean data 
library(here) # locate the file path
clean_data<- read.csv(here::here("inputs/DATA/clean_data.csv"))
```

## T-test
## correlation model
## propensity score matching
## regression model
